asc_file_database

### 2019-03-07 src/asc_file_database.Rmd
arghhhhh!!!

asclayer <- crossing(ascyears, ascmonths, ascdepths)
asclayer$stackname <- paste0("st", asclayer$ascyears, asclayer$ascmonths, asclayer$ascdepths) #this creates the name of the stack that will be used
asclayer$temp_depth <- NA
asclayer$temp_surface <- NA
asclayer$chl_depth <- NA
asclayer$chl_surface <- NA
asclayer$o2_depth <- NA
asclayer$o2_surface <- NA
asclayer$salinity_depth <- NA
asclayer$salinity_surface <- NA
asclayer$ssh_surface <- NA
asclayer$mlp_surface <- NA
asclayer$nao_sample <- NA
asclayer$nao_prev <- NA
asclayer$nao_winter <- NA
asclayer$amo_sample <- NA
asclayer$amo_prev <- NA
asclayer$amo_winter <- NA

ascname <- list.files("../data/env/ascii/", pattern = "*.asc", full.names = FALSE)    # this folder currently contains other dummy files. its just a test to automate stacks
ascpath <- list.files("../data/env/ascii/", pattern = "*.asc", full.names = TRUE)    # this folder currently contains other dummy files. its just a test to automate stacks

tempvar <- "temp"
chlvar <- "chl"
o2var <- "o2"
salvar <- "salinity"
mlpvar <- "mlp"
sshvar <- "ssh"
naosamplevar <- "naosample"
amosamplevar <- "amosample"
naoprev <- "naoprev"
amoprev <- "amoprev"
naowinter <- "naowinter"
amowinter <- "amowinter"
climatedepth <- "1"
surfacevar <- "0.50576"

@@

    for (k in 1:length(ascname)){
        ascyear <- (sapply(strsplit(ascname[k], "_"), "[[", 1))
        ascmonth <- (sapply(strsplit(ascname[k], "_"), "[[", 2))
        ascdepth <- (sapply(strsplit(ascname[k], "_"), "[[", 4))
        ascdepth <- gsub(".asc", "", ascdepth)
        ascvar <- (sapply(strsplit(ascname[k], "_"), "[[", 3))
        ascfile <- ascpath[k]
        print(ascfile)

        if (ascyear == year & ascmonth == month & ascvar == tempvar & ascdepth == depth){
          asclayer$temp_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == tempvar & ascdepth == surfacevar){
          asclayer$temp_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == salvar & ascdepth == depth){
          asclayer$temp_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == salvar & ascdepth == surfacevar){
          asclayer$salinity_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == chlvar & ascdepth == depth){
          asclayer$chl_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == chlvar & ascdepth == surfacevar){
          asclayer$chl_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == o2lvar & ascdepth == depth){
          asclayer$temp_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == o2var & ascdepth == surfacevar){
          asclayer$o2_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == mlpvar){
          asclayer$mlp_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == sshvar){
          asclayer$ssh_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == naosample){
          asclayer$nao_sample[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == amosample){
          asclayer$amo_sample[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == naoprev){
          asclayer$nao_prev[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == amoprev){
          asclayer$amo_prev[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == naowinter){
          asclayer$nao_winter[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == amowinter){
          asclayer$amo_winter[i] <- ascfile
        }
    }
  write.csv(asclayer, "../data/env/asc_layerlist.csv", row.names = TRUE)
}
```

>>>>

asclayerall <- crossing(ascyears, ascmonths, ascdepths)
asclayerall$stackname <- paste0("st", asclayerall$ascyears, asclayerall$ascmonths, asclayerall$ascdepths) #this creates the name of the stack that will be used
asclayerall$temp_depth <- NA
asclayerall$temp_surface <- NA
asclayerall$chl_depth <- NA
asclayerall$chl_surface <- NA
asclayerall$o2_depth <- NA
asclayerall$o2_surface <- NA
asclayerall$salinity_depth <- NA
asclayerall$salinity_surface <- NA
asclayerall$ssh_surface <- NA
asclayerall$mlp_surface <- NA
asclayerall$nao_sample <- NA
asclayerall$nao_prev <- NA
asclayerall$nao_winter <- NA
asclayerall$amo_sample <- NA
asclayerall$amo_prev <- NA
asclayerall$amo_winter <- NA

```

```{r}
#!!!!!!  CHANGE ASCNAME, ASCPATH AND CSV FILE NAME

asclayer <- subset(asclayerall, ascyears == 1998)

ascname <- list.files("../data/env/ascii/ascii1998/", pattern = "*.asc", full.names = FALSE)    # this folder currently contains other dummy files. its just a test to automate stacks
ascpath <- list.files("../data/env/ascii/ascii1998/", pattern = "*.asc", full.names = TRUE)    # this folder currently contains other dummy files. its just a test to automate stacks

tempvar <- "temp.nc"
chlvar <- "chl.nc"
o2var <- "o2.nc"
salvar <- "salinity.nc"
mlpvar <- "mlp.nc"
sshvar <- "ssh.nc"
naosamplevar <- "naosample"
amosamplevar <- "amosample"
naoprevvar <- "naoprev"
amoprevvar <- "amoprev"
naowintervar <- "naowinter"
amowintervar <- "amowinter"
surfacevar <- "0.50576"

@@

    for (k in 1:length(ascname)){
        ascyear <- (sapply(strsplit(ascname[k], "_"), "[[", 1))
        ascmonth <- (sapply(strsplit(ascname[k], "_"), "[[", 2))
        ascvar <- (sapply(strsplit(ascname[k], "_"), "[[", 3))
        ascdepth <- (sapply(strsplit(ascname[k], "_"), "[[", 4))
        ascdepth <- gsub(".asc", "", ascdepth)
        ascfile <- ascpath[k]

        if (ascyear == year & ascmonth == month & ascvar == tempvar & ascdepth == depth){
          asclayer$temp_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == tempvar & ascdepth == surfacevar){
          asclayer$temp_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == salvar & ascdepth == depth){
          asclayer$salinity_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == salvar & ascdepth == surfacevar){
          asclayer$salinity_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == chlvar & ascdepth == depth){
          asclayer$chl_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == chlvar & ascdepth == surfacevar){
          asclayer$chl_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == o2var & ascdepth == depth){
          asclayer$o2_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == o2var & ascdepth == surfacevar){
          asclayer$o2_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == mlpvar){
          asclayer$mlp_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == sshvar){
          asclayer$ssh_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == naosamplevar){
          asclayer$nao_sample[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == amosamplevar){
          asclayer$amo_sample[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == naoprevvar){
          asclayer$nao_prev[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == amoprevvar){
          asclayer$amo_prev[i] <- ascfile
        } else if(ascyear == year & ascvar == naowintervar){
          asclayer$nao_winter[i] <- ascfile
        } else if(ascyear == year & ascvar == amowintervar){
          asclayer$amo_winter[i] <- ascfile
        }
    }
  write.csv(asclayer, "../data/env/asc_layerlist1998.csv", row.names = TRUE)
}
```

```{r}
#!!!!!!  CHANGE ASCLAYER ASCNAME, ASCPATH AND CSV FILE NAME

asclayer <- subset(asclayerall, ascyears == 1999)

ascname <- list.files("../data/env/ascii/ascii1999/", pattern = "*.asc", full.names = FALSE)    # this folder currently contains other dummy files. its just a test to automate stacks
ascpath <- list.files("../data/env/ascii/ascii1999/", pattern = "*.asc", full.names = TRUE)    # this folder currently contains other dummy files. its just a test to automate stacks

tempvar <- "temp.nc"
chlvar <- "chl.nc"
o2var <- "o2.nc"
salvar <- "salinity.nc"
mlpvar <- "mlp.nc"
sshvar <- "ssh.nc"
naosamplevar <- "naosample"
amosamplevar <- "amosample"
naoprevvar <- "naoprev"
amoprevvar <- "amoprev"
naowintervar <- "naowinter"
amowintervar <- "amowinter"
surfacevar <- "0.50576"

    for (k in 1:length(ascname)){
        ascyear <- (sapply(strsplit(ascname[k], "_"), "[[", 1))
        ascmonth <- (sapply(strsplit(ascname[k], "_"), "[[", 2))
        ascvar <- (sapply(strsplit(ascname[k], "_"), "[[", 3))
        ascdepth <- (sapply(strsplit(ascname[k], "_"), "[[", 4))
        ascdepth <- gsub(".asc", "", ascdepth)
        ascfile <- ascpath[k]

        if (ascyear == year & ascmonth == month & ascvar == tempvar & ascdepth == depth){
          asclayer$temp_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == tempvar & ascdepth == surfacevar){
          asclayer$temp_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == salvar & ascdepth == depth){
          asclayer$salinity_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == salvar & ascdepth == surfacevar){
          asclayer$salinity_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == chlvar & ascdepth == depth){
          asclayer$chl_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == chlvar & ascdepth == surfacevar){
          asclayer$chl_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == o2var & ascdepth == depth){
          asclayer$o2_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == o2var & ascdepth == surfacevar){
          asclayer$o2_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == mlpvar){
          asclayer$mlp_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == sshvar){
          asclayer$ssh_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == naosamplevar){
          asclayer$nao_sample[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == amosamplevar){
          asclayer$amo_sample[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == naoprevvar){
          asclayer$nao_prev[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == amoprevvar){
          asclayer$amo_prev[i] <- ascfile
        } else if(ascyear == year & ascvar == naowintervar){
          asclayer$nao_winter[i] <- ascfile
        } else if(ascyear == year & ascvar == amowintervar){
          asclayer$amo_winter[i] <- ascfile
        }
    }
  write.csv(asclayer, "../data/env/asc_layerlist1999.csv", row.names = TRUE)
}
```

```{r}
#!!!!!!  CHANGE ASCNAME, ASCPATH AND CSV FILE NAME

asclayer <- subset(asclayerall, ascyears == 2000)

ascname <- list.files("../data/env/ascii/ascii2000/", pattern = "*.asc", full.names = FALSE)    # this folder currently contains other dummy files. its just a test to automate stacks
ascpath <- list.files("../data/env/ascii/ascii2000/", pattern = "*.asc", full.names = TRUE)    # this folder currently contains other dummy files. its just a test to automate stacks

tempvar <- "temp.nc"
chlvar <- "chl.nc"
o2var <- "o2.nc"
salvar <- "salinity.nc"
mlpvar <- "mlp.nc"
sshvar <- "ssh.nc"
naosamplevar <- "naosample"
amosamplevar <- "amosample"
naoprevvar <- "naoprev"
amoprevvar <- "amoprev"
naowintervar <- "naowinter"
amowintervar <- "amowinter"
surfacevar <- "0.50576"

    for (k in 1:length(ascname)){
        ascyear <- (sapply(strsplit(ascname[k], "_"), "[[", 1))
        ascmonth <- (sapply(strsplit(ascname[k], "_"), "[[", 2))
        ascvar <- (sapply(strsplit(ascname[k], "_"), "[[", 3))
        ascdepth <- (sapply(strsplit(ascname[k], "_"), "[[", 4))
        ascdepth <- gsub(".asc", "", ascdepth)
        ascfile <- ascpath[k]

        if (ascyear == year & ascmonth == month & ascvar == tempvar & ascdepth == depth){
          asclayer$temp_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == tempvar & ascdepth == surfacevar){
          asclayer$temp_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == salvar & ascdepth == depth){
          asclayer$salinity_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == salvar & ascdepth == surfacevar){
          asclayer$salinity_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == chlvar & ascdepth == depth){
          asclayer$chl_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == chlvar & ascdepth == surfacevar){
          asclayer$chl_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == o2var & ascdepth == depth){
          asclayer$o2_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == o2var & ascdepth == surfacevar){
          asclayer$o2_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == mlpvar){
          asclayer$mlp_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == sshvar){
          asclayer$ssh_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == naosamplevar){
          asclayer$nao_sample[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == amosamplevar){
          asclayer$amo_sample[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == naoprevvar){
          asclayer$nao_prev[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == amoprevvar){
          asclayer$amo_prev[i] <- ascfile
        } else if(ascyear == year & ascvar == naowintervar){
          asclayer$nao_winter[i] <- ascfile
        } else if(ascyear == year & ascvar == amowintervar){
          asclayer$amo_winter[i] <- ascfile
        }
    }
  write.csv(asclayer, "../data/env/asc_layerlist2000.csv", row.names = TRUE)
}
```

```{r}
#!!!!!!  CHANGE ASCNAME, ASCPATH AND CSV FILE NAME

asclayer <- subset(asclayerall, ascyears == 2001)

ascname <- list.files("../data/env/ascii/ascii2001/", pattern = "*.asc", full.names = FALSE)    # this folder currently contains other dummy files. its just a test to automate stacks
ascpath <- list.files("../data/env/ascii/ascii2001/", pattern = "*.asc", full.names = TRUE)    # this folder currently contains other dummy files. its just a test to automate stacks

tempvar <- "temp.nc"
chlvar <- "chl.nc"
o2var <- "o2.nc"
salvar <- "salinity.nc"
mlpvar <- "mlp.nc"
sshvar <- "ssh.nc"
naosamplevar <- "naosample"
amosamplevar <- "amosample"
naoprevvar <- "naoprev"
amoprevvar <- "amoprev"
naowintervar <- "naowinter"
amowintervar <- "amowinter"
surfacevar <- "0.50576"

    for (k in 1:length(ascname)){
        ascyear <- (sapply(strsplit(ascname[k], "_"), "[[", 1))
        ascmonth <- (sapply(strsplit(ascname[k], "_"), "[[", 2))
        ascvar <- (sapply(strsplit(ascname[k], "_"), "[[", 3))
        ascdepth <- (sapply(strsplit(ascname[k], "_"), "[[", 4))
        ascdepth <- gsub(".asc", "", ascdepth)
        ascfile <- ascpath[k]

        if (ascyear == year & ascmonth == month & ascvar == tempvar & ascdepth == depth){
          asclayer$temp_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == tempvar & ascdepth == surfacevar){
          asclayer$temp_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == salvar & ascdepth == depth){
          asclayer$salinity_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == salvar & ascdepth == surfacevar){
          asclayer$salinity_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == chlvar & ascdepth == depth){
          asclayer$chl_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == chlvar & ascdepth == surfacevar){
          asclayer$chl_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == o2var & ascdepth == depth){
          asclayer$o2_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == o2var & ascdepth == surfacevar){
          asclayer$o2_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == mlpvar){
          asclayer$mlp_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == sshvar){
          asclayer$ssh_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == naosamplevar){
          asclayer$nao_sample[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == amosamplevar){
          asclayer$amo_sample[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == naoprevvar){
          asclayer$nao_prev[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == amoprevvar){
          asclayer$amo_prev[i] <- ascfile
        } else if(ascyear == year & ascvar == naowintervar){
          asclayer$nao_winter[i] <- ascfile
        } else if(ascyear == year & ascvar == amowintervar){
          asclayer$amo_winter[i] <- ascfile
        }
    }
  write.csv(asclayer, "../data/env/asc_layerlist2001.csv", row.names = TRUE)
}
```

```{r}
#!!!!!!  CHANGE ASCNAME, ASCPATH AND CSV FILE NAME

asclayer <- subset(asclayerall, ascyears == 2002)

ascname <- list.files("../data/env/ascii/ascii2002/", pattern = "*.asc", full.names = FALSE)    # this folder currently contains other dummy files. its just a test to automate stacks
ascpath <- list.files("../data/env/ascii/ascii2002/", pattern = "*.asc", full.names = TRUE)    # this folder currently contains other dummy files. its just a test to automate stacks

tempvar <- "temp.nc"
chlvar <- "chl.nc"
o2var <- "o2.nc"
salvar <- "salinity.nc"
mlpvar <- "mlp.nc"
sshvar <- "ssh.nc"
naosamplevar <- "naosample"
amosamplevar <- "amosample"
naoprevvar <- "naoprev"
amoprevvar <- "amoprev"
naowintervar <- "naowinter"
amowintervar <- "amowinter"
surfacevar <- "0.50576"

    for (k in 1:length(ascname)){
        ascyear <- (sapply(strsplit(ascname[k], "_"), "[[", 1))
        ascmonth <- (sapply(strsplit(ascname[k], "_"), "[[", 2))
        ascvar <- (sapply(strsplit(ascname[k], "_"), "[[", 3))
        ascdepth <- (sapply(strsplit(ascname[k], "_"), "[[", 4))
        ascdepth <- gsub(".asc", "", ascdepth)
        ascfile <- ascpath[k]

        if (ascyear == year & ascmonth == month & ascvar == tempvar & ascdepth == depth){
          asclayer$temp_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == tempvar & ascdepth == surfacevar){
          asclayer$temp_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == salvar & ascdepth == depth){
          asclayer$salinity_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == salvar & ascdepth == surfacevar){
          asclayer$salinity_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == chlvar & ascdepth == depth){
          asclayer$chl_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == chlvar & ascdepth == surfacevar){
          asclayer$chl_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == o2var & ascdepth == depth){
          asclayer$o2_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == o2var & ascdepth == surfacevar){
          asclayer$o2_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == mlpvar){
          asclayer$mlp_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == sshvar){
          asclayer$ssh_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == naosamplevar){
          asclayer$nao_sample[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == amosamplevar){
          asclayer$amo_sample[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == naoprevvar){
          asclayer$nao_prev[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == amoprevvar){
          asclayer$amo_prev[i] <- ascfile
        } else if(ascyear == year & ascvar == naowintervar){
          asclayer$nao_winter[i] <- ascfile
        } else if(ascyear == year & ascvar == amowintervar){
          asclayer$amo_winter[i] <- ascfile
        }
    }
  write.csv(asclayer, "../data/env/asc_layerlist2002.csv", row.names = TRUE)
}
```

```{r}
#!!!!!!  CHANGE ASCNAME, ASCPATH AND CSV FILE NAME

asclayer <- subset(asclayerall, ascyears == 2003)

ascname <- list.files("../data/env/ascii/ascii2003/", pattern = "*.asc", full.names = FALSE)    # this folder currently contains other dummy files. its just a test to automate stacks
ascpath <- list.files("../data/env/ascii/ascii2003/", pattern = "*.asc", full.names = TRUE)    # this folder currently contains other dummy files. its just a test to automate stacks

tempvar <- "temp.nc"
chlvar <- "chl.nc"
o2var <- "o2.nc"
salvar <- "salinity.nc"
mlpvar <- "mlp.nc"
sshvar <- "ssh.nc"
naosamplevar <- "naosample"
amosamplevar <- "amosample"
naoprevvar <- "naoprev"
amoprevvar <- "amoprev"
naowintervar <- "naowinter"
amowintervar <- "amowinter"
surfacevar <- "0.50576"

    for (k in 1:length(ascname)){
        ascyear <- (sapply(strsplit(ascname[k], "_"), "[[", 1))
        ascmonth <- (sapply(strsplit(ascname[k], "_"), "[[", 2))
        ascvar <- (sapply(strsplit(ascname[k], "_"), "[[", 3))
        ascdepth <- (sapply(strsplit(ascname[k], "_"), "[[", 4))
        ascdepth <- gsub(".asc", "", ascdepth)
        ascfile <- ascpath[k]

        if (ascyear == year & ascmonth == month & ascvar == tempvar & ascdepth == depth){
          asclayer$temp_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == tempvar & ascdepth == surfacevar){
          asclayer$temp_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == salvar & ascdepth == depth){
          asclayer$salinity_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == salvar & ascdepth == surfacevar){
          asclayer$salinity_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == chlvar & ascdepth == depth){
          asclayer$chl_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == chlvar & ascdepth == surfacevar){
          asclayer$chl_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == o2var & ascdepth == depth){
          asclayer$o2_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == o2var & ascdepth == surfacevar){
          asclayer$o2_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == mlpvar){
          asclayer$mlp_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == sshvar){
          asclayer$ssh_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == naosamplevar){
          asclayer$nao_sample[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == amosamplevar){
          asclayer$amo_sample[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == naoprevvar){
          asclayer$nao_prev[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == amoprevvar){
          asclayer$amo_prev[i] <- ascfile
        } else if(ascyear == year & ascvar == naowintervar){
          asclayer$nao_winter[i] <- ascfile
        } else if(ascyear == year & ascvar == amowintervar){
          asclayer$amo_winter[i] <- ascfile
        }
    }
  write.csv(asclayer, "../data/env/asc_layerlist2003.csv", row.names = TRUE)
}
```

```{r}
#!!!!!!  CHANGE ASCNAME, ASCPATH AND CSV FILE NAME

asclayer <- subset(asclayerall, ascyears == 2004)

ascname <- list.files("../data/env/ascii/ascii2004/", pattern = "*.asc", full.names = FALSE)    # this folder currently contains other dummy files. its just a test to automate stacks
ascpath <- list.files("../data/env/ascii/ascii2004/", pattern = "*.asc", full.names = TRUE)    # this folder currently contains other dummy files. its just a test to automate stacks

tempvar <- "temp.nc"
chlvar <- "chl.nc"
o2var <- "o2.nc"
salvar <- "salinity.nc"
mlpvar <- "mlp.nc"
sshvar <- "ssh.nc"
naosamplevar <- "naosample"
amosamplevar <- "amosample"
naoprevvar <- "naoprev"
amoprevvar <- "amoprev"
naowintervar <- "naowinter"
amowintervar <- "amowinter"
surfacevar <- "0.50576"

    for (k in 1:length(ascname)){
        ascyear <- (sapply(strsplit(ascname[k], "_"), "[[", 1))
        ascmonth <- (sapply(strsplit(ascname[k], "_"), "[[", 2))
        ascvar <- (sapply(strsplit(ascname[k], "_"), "[[", 3))
        ascdepth <- (sapply(strsplit(ascname[k], "_"), "[[", 4))
        ascdepth <- gsub(".asc", "", ascdepth)
        ascfile <- ascpath[k]

        if (ascyear == year & ascmonth == month & ascvar == tempvar & ascdepth == depth){
          asclayer$temp_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == tempvar & ascdepth == surfacevar){
          asclayer$temp_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == salvar & ascdepth == depth){
          asclayer$salinity_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == salvar & ascdepth == surfacevar){
          asclayer$salinity_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == chlvar & ascdepth == depth){
          asclayer$chl_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == chlvar & ascdepth == surfacevar){
          asclayer$chl_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == o2var & ascdepth == depth){
          asclayer$o2_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == o2var & ascdepth == surfacevar){
          asclayer$o2_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == mlpvar){
          asclayer$mlp_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == sshvar){
          asclayer$ssh_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == naosamplevar){
          asclayer$nao_sample[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == amosamplevar){
          asclayer$amo_sample[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == naoprevvar){
          asclayer$nao_prev[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == amoprevvar){
          asclayer$amo_prev[i] <- ascfile
        } else if(ascyear == year & ascvar == naowintervar){
          asclayer$nao_winter[i] <- ascfile
        } else if(ascyear == year & ascvar == amowintervar){
          asclayer$amo_winter[i] <- ascfile
        }
    }
  write.csv(asclayer, "../data/env/asc_layerlist2004.csv", row.names = TRUE)
}
```

```{r}
#!!!!!!  CHANGE ASCNAME, ASCPATH AND CSV FILE NAME

asclayer <- subset(asclayerall, ascyears == 2005)

ascname <- list.files("../data/env/ascii/ascii2005/", pattern = "*.asc", full.names = FALSE)    # this folder currently contains other dummy files. its just a test to automate stacks
ascpath <- list.files("../data/env/ascii/ascii2005/", pattern = "*.asc", full.names = TRUE)    # this folder currently contains other dummy files. its just a test to automate stacks

tempvar <- "temp.nc"
chlvar <- "chl.nc"
o2var <- "o2.nc"
salvar <- "salinity.nc"
mlpvar <- "mlp.nc"
sshvar <- "ssh.nc"
naosamplevar <- "naosample"
amosamplevar <- "amosample"
naoprevvar <- "naoprev"
amoprevvar <- "amoprev"
naowintervar <- "naowinter"
amowintervar <- "amowinter"
surfacevar <- "0.50576"

    for (k in 1:length(ascname)){
        ascyear <- (sapply(strsplit(ascname[k], "_"), "[[", 1))
        ascmonth <- (sapply(strsplit(ascname[k], "_"), "[[", 2))
        ascvar <- (sapply(strsplit(ascname[k], "_"), "[[", 3))
        ascdepth <- (sapply(strsplit(ascname[k], "_"), "[[", 4))
        ascdepth <- gsub(".asc", "", ascdepth)
        ascfile <- ascpath[k]

        if (ascyear == year & ascmonth == month & ascvar == tempvar & ascdepth == depth){
          asclayer$temp_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == tempvar & ascdepth == surfacevar){
          asclayer$temp_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == salvar & ascdepth == depth){
          asclayer$salinity_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == salvar & ascdepth == surfacevar){
          asclayer$salinity_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == chlvar & ascdepth == depth){
          asclayer$chl_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == chlvar & ascdepth == surfacevar){
          asclayer$chl_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == o2var & ascdepth == depth){
          asclayer$o2_depth[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == o2var & ascdepth == surfacevar){
          asclayer$o2_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == mlpvar){
          asclayer$mlp_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == sshvar){
          asclayer$ssh_surface[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == naosamplevar){
          asclayer$nao_sample[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == amosamplevar){
          asclayer$amo_sample[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == naoprevvar){
          asclayer$nao_prev[i] <- ascfile
        } else if(ascyear == year & ascmonth == month & ascvar == amoprevvar){
          asclayer$amo_prev[i] <- ascfile
        } else if(ascyear == year & ascvar == naowintervar){
          asclayer$nao_winter[i] <- ascfile
        } else if(ascyear == year & ascvar == amowintervar){
          asclayer$amo_winter[i] <- ascfile
        }
    }
  write.csv(asclayer, "../data/env/asc_layerlist2005.csv", row.names = TRUE)
}
```

```{r}
#!!!!!!  CHANGE ASCNAME, ASCPATH AND CSV FILE NAME

asclayer <- subset(asclayerall, ascyears == 2006)

ascname <- list.files("../data/env/ascii/ascii2006/", pattern = "*.asc", full.names = FALSE)    # this folder currently contains other dummy files. its just a test to automate stacks
ascpath <- list.files("../data/env/ascii/ascii2006/", pattern = "*.asc", full.names = TRUE)    # this folder currently contains other dummy files. its just a test to automate stacks

tempvar <- "temp.nc"
chlvar <- "chl.nc"
o2var <- "o2.nc"
salvar <- "salinity.nc"
mlpvar <- "mlp.nc"
sshvar <- "ssh.nc"
naosamplevar <- "naosample"
amosamplevar <- "amosample"
naoprevvar <- "naoprev"
amoprevvar <- "amoprev"
naowintervar <- "naowinter"
amowintervar <- "amowinter"
surfacevar <- "0.50576"
